---
title: "Automatic report on the impact of coronavirus on unemployment"
author: "Claudia Słaboń, Kateryna Kondratovych"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r libraries, include=FALSE}
library(ggthemes)
library(tibble)
library(lubridate)
library(ggpubr)
library(reshape)
library(scales)
library(plotly)
library(tidyverse)
library(rvest)
library(rlist)
library(stringi)
library(htmltab)
library(zoo)
library(dplyr)
library(tidyr)
library(xts)
library(dygraphs)
library(RColorBrewer)
library(ggplot2)
library(rgdal)
library(sf)
library(readxl)
library(viridis)
library(cowplot)
library(forecast) 

```

## COVID-19 and it’s impact on unemployment rate
<font size="4">
The first cases of COVID-19 comes from China (Wuhan) and were discovered in November 2019. From the beginning of the 2020 new outbreaks of the coronavirus have started to appear in other countries. The pandemic spread around the world rapidly. The discovery of the easily contagious virus forced on the world's government to take an fast and unconventional actions. Many countries have closed their borders and introduced lockdown. Due to such actions many economies suffer from a pandemic. \
The aim of this report is to discover whether the COVID-19 had an impact on unemployment. Firsly, it will be examined from the point of view of OECD countries, G7 countries, the USA. After that, the situation in Poland will be presented.

Dataset sources: \
- Wikipedia information regarding coronavirus cases. \
- Monthly unemployment rate in OECD countries comes from the OECD website. \
- Poland unemployment rate in voivodships comes from Poland's Central Statistical Office. \
- Poland map was built from dataset introduced during the classes. \
<font>
```{r datasets, echo=FALSE, results='hide'}
# Datasets that should be updated
data_unemp <- read.csv("Dane/DP_LIVE_09062021091719878.csv")
data_covid <- read.csv("Dane/covid-19-all.csv")

rate <- read.csv('Dane/MW_new.csv')
rate <- rate[c(1,3,6,7)]
rate <- transform(rate, TIME = as.Date(as.yearmon(TIME)))

eduk <- read.csv('Dane/eduk.csv',stringsAsFactors = FALSE)
eduk <- eduk[c(1,3,6,7)]
eduk <- transform(eduk, TIME = as.Date(as.yearmon(TIME)))

agek <- read.csv('Dane/agek.csv')
agek <- agek[c(1,3,6,7)]
agek <- transform(agek, TIME = as.Date(as.yearmon(TIME)))

unemp <- read.csv('Dane/unemp.csv')
unemp <- unemp[c(1,6,7)]
unemp <- transform(unemp, TIME = as.Date(as.yearmon(TIME)))
```

# COVID-19 spread

```{r}
# Statistics - updated from Wikipedia

url <- "https://en.m.wikipedia.org/wiki/COVID-19_pandemic_by_country_and_territory#"
# Scraping Wikipedia page using CSS selector in order to obtain current number of COVID cases and deaths
current_cases_all <- url %>%
  read_html() %>%
  html_node(css = "#thetable > tbody > tr.sorttop > th:nth-child(3)") %>%
  html_text()

current_cases_all <- as.numeric(gsub(",", "", current_cases_all))

current_deaths_all <- url %>%
  read_html() %>%
  html_node(css = "#thetable > tbody > tr.sorttop > th:nth-child(4)") %>%
  html_text()

current_deaths_all <- as.numeric(gsub(",", "", current_deaths_all))

# Creating new date frame containing 3 countries with the highest number of COVID cases from Wikipedia
top_covid_countries <- data.frame(Country = character(), cases = character(), stringsAsFactors = FALSE)
# Based on tested CSS variable i needs to start from 3
i <- 3

for (j in 1:3) {
  top_covid_countries <- rbind(
    top_covid_countries,
    data.frame(
      Country = url %>%
        read_html() %>%
        html_node(css = paste0("#thetable > tbody > tr:nth-child(", i, ") > th:nth-child(2) > a")) %>%
        html_text(),
      cases = url %>%
        read_html() %>%
        html_node(css = paste0("#thetable > tbody > tr:nth-child(", i, ") > td:nth-child(3)")) %>%
        html_text()
    )
  )

  i <- i + 1
}


```
<font size="4">
Although, the first cases of coronavirus were discover in China in the late of 2019, the pandemic rapidly spread around the whole world. Currently, there is **`r format(current_cases_all,big.mark=",",scientific=FALSE)`** coronavirus cases, **`r format(current_deaths_all,big.mark=",",scientific=FALSE)`** people died (`r format(Sys.time(), '%d %B, %Y')` update). \

Official top 3 countries with **highest** COVID-19 cases number: \
- `r top_covid_countries[1,1]` (`r toString(top_covid_countries[1,2])` cases), \
- `r top_covid_countries[2,1]` (`r toString(top_covid_countries[2,2])` cases), \
- `r top_covid_countries[3,1]` (`r toString(top_covid_countries[3,2])` cases). \
<font>
```{r, echo=FALSE, results='hide'}
# Selecting 3 month before newest data of the unemployment analysis in OECD countries. Choosing 3 month before newest data date can prevent from missing data in some countries.
unemp_analysis_date <- data_unemp %>% select(TIME) %>% distinct() %>% pull(1) %>% sort()
n <- nth(unemp_analysis_date, -3) 
n
```

# Unemployment rate in OECD countries
<font size="4">
Below graphs present the situation of unemployment rate in OECD countries. It means that the unemployment rate is captured in 37 countries.
<font>
```{r oecd, echo=FALSE, fig.align='center', results='hide', message = FALSE, fig.width = 8, fig.height = 8}
colnames(data_unemp)[1] <- "Country"

# Conducting analysis between 15 months before newest data and 3 month before newest data.
# Excluding every record except country.

# 15 months before newest data graph
plot_unemp_previous <- data_unemp %>%
  filter(TIME == nth(unemp_analysis_date, -15) & Country != "G-7" & Country != "EU28" & Country != "EA19" & Country != "EU27_2020" & Country != "OECD") %>%
  select(Country, Value) %>%
  arrange(desc(Value)) %>%
  top_n(15) %>%
  arrange(Value) %>%
  mutate(Country = factor(Country, levels = .$Country)) %>%
  ggplot(aes(x = Country, y = Value)) +
  geom_segment(aes(x = Country, xend = Country, y = 0, yend = Value), color = "black") +
  scale_y_continuous(labels = function(x) paste0(x, "%")) +
  geom_point(color = "skyblue", size = 4) +
  theme_light() +
  coord_flip() +
  labs(title = paste0("Highest unemployment rate in ", nth(unemp_analysis_date, -15))) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = 0.5)
  )

# 3 months before newest, available data - graph
plot_unemp_current <-
  data_unemp %>%
  filter(TIME == nth(unemp_analysis_date, -3) & Country != "G-7" & Country != "EU28" & Country != "EA19" & Country != "EU27_2020" & Country != "OECD") %>%
  select(Country, Value) %>%
  arrange(desc(Value)) %>%
  top_n(15) %>%
  arrange(Value) %>%
  mutate(Country = factor(Country, levels = .$Country)) %>%
  ggplot(aes(x = Country, y = Value)) +
  geom_segment(aes(x = Country, xend = Country, y = 0, yend = Value), color = "black") +
  scale_y_continuous(labels = function(x) paste0(x, "%")) +
  geom_point(color = "skyblue", size = 4) +
  theme_light() +
  coord_flip() +
  labs(title = paste0("Highest unemployment rate in ", nth(unemp_analysis_date, -3))) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = 0.5)
  )

# Graph which shows difference between these 2 dates
plot_unem_dates_diff <- data_unemp %>%
  filter(TIME == nth(unemp_analysis_date, -15) | TIME == nth(unemp_analysis_date, -3)) %>%
  select(Country, TIME, Value) %>%
  cast(Country ~ TIME) %>%
  filter(Country != "G-7" & Country != "EU28" & Country != "EA19" & Country != "EU27_2020" & Country != "OECD") %>%
  select(1, Previous_date = 2, Current_date = 3) %>%
  mutate(diff = abs(Current_date - Previous_date)) %>%
  arrange(desc(diff)) %>%
  mutate(Country = factor(Country, levels = .$Country)) %>%
  top_n(15) %>%
  ggplot(aes(x = factor(Country), y = diff)) +
  geom_bar(na.rm = TRUE, width = 0.7, stat = "identity", aes(fill = diff)) +
  geom_text(aes(label = paste0(round(diff, 1), "%")), vjust = -0.25, size = 3) +
  scale_y_continuous(labels = function(x) paste0(x, "%")) +
  scale_fill_gradient2(low = "lightblue", mid = "lightblue", high = "#1167b1") +
  labs(
    title = "The greatest change in unemployment rate between newer and older chosen date",
    caption = "Data comes from OECD which monitores unemployment in 37 countries."
  ) +
  theme(
    legend.title = element_blank(),
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.caption = element_text(hjust = 0)
  )

# Combining 3 graphs into 1 to make nicer visualization
ggarrange(ggarrange(plot_unemp_previous, plot_unemp_current, ncol = 2),
  plot_unem_dates_diff,
  nrow = 2
)


# Variable that shows unemployment changed
if(mean(plot_unemp_current[["data"]][["Value"]]) < mean(plot_unemp_previous[["data"]][["Value"]])){
  change_between_dates <- 'decreased'
} else if(mean(plot_unemp_current[["data"]][["Value"]]) > mean(plot_unemp_previous[["data"]][["Value"]])){
  change_between_dates <- 'increased'  
} else{
  change_between_dates <- 'have not changed'   
}


```
<font size="4">
The first lollipop graph shows 15 highest unemployment rates among OECD countries in `r nth(unemp_analysis_date, -15)`. Country with the highest unemployment rate is `r nth(plot_unemp_previous[["data"]][["Country"]],-1)` (around `r paste0(round(nth(plot_unemp_previous[["data"]][["Value"]],-1),1),"%")`), then `r nth(plot_unemp_previous[["data"]][["Country"]],-2)` (around `r paste0(round(nth(plot_unemp_previous[["data"]][["Value"]],-2),1),"%")`) and `r nth(plot_unemp_previous[["data"]][["Country"]],-3)` (around `r paste0(round(nth(plot_unemp_previous[["data"]][["Value"]],-3),1),"%")`). \
The second lollipop graph shows 15 largest unemployment rate in `r nth(unemp_analysis_date, -2)`. During that 1 year it can be observed that on average unemployment rate **`r change_between_dates`** in almost every country. \
It needs to be emphasize that there are some countries that have a problem with high unemployment rate independently from pandemic. Due to that, one can find the barchart more informative for that kind of analysis. From that graph one can capture that the highest change between `r nth(unemp_analysis_date, -15)` and `r nth(unemp_analysis_date, -3)` is observed in `r nth(plot_unem_dates_diff[["data"]][["Country"]],1)`, then `r nth(plot_unem_dates_diff[["data"]][["Country"]],2)` and `r nth(plot_unem_dates_diff[["data"]][["Country"]],3)`.
<font>

```{r names, echo=FALSE}

# Changing countries' names to create nicer visualization
levels(data_unemp$Country)[levels(data_unemp$Country)=='POL'] <- 'Poland'
levels(data_unemp$Country)[levels(data_unemp$Country)=='AUS'] <- 'Australia'
levels(data_unemp$Country)[levels(data_unemp$Country)=='AUT'] <- 'Austria'
levels(data_unemp$Country)[levels(data_unemp$Country)=='BEL'] <- 'Belgium'
levels(data_unemp$Country)[levels(data_unemp$Country)=='CAN'] <- 'Canada'
levels(data_unemp$Country)[levels(data_unemp$Country)=='CZE'] <- 'Czech Rep.'
levels(data_unemp$Country)[levels(data_unemp$Country)=='DNK'] <- 'Denmark'
levels(data_unemp$Country)[levels(data_unemp$Country)=='FIN'] <- 'Finland'
levels(data_unemp$Country)[levels(data_unemp$Country)=='FRA'] <- 'France'
levels(data_unemp$Country)[levels(data_unemp$Country)=='DEU'] <- 'Germany'
levels(data_unemp$Country)[levels(data_unemp$Country)=='GRC'] <- 'Greece'
levels(data_unemp$Country)[levels(data_unemp$Country)=='HUN'] <- 'Hungary'
levels(data_unemp$Country)[levels(data_unemp$Country)=='ISL'] <- 'Iceland'
levels(data_unemp$Country)[levels(data_unemp$Country)=='IRL'] <- 'Ireland'
levels(data_unemp$Country)[levels(data_unemp$Country)=='ITA'] <- 'Italy'
levels(data_unemp$Country)[levels(data_unemp$Country)=='JPN'] <- 'Japan'
levels(data_unemp$Country)[levels(data_unemp$Country)=='KOR'] <- 'South Korea'
levels(data_unemp$Country)[levels(data_unemp$Country)=='LUX'] <- 'Luxembourg'
levels(data_unemp$Country)[levels(data_unemp$Country)=='MEX'] <- 'Mexico'
levels(data_unemp$Country)[levels(data_unemp$Country)=='NLD'] <- 'Netherlands'
levels(data_unemp$Country)[levels(data_unemp$Country)=='NOR'] <- 'Norway'
levels(data_unemp$Country)[levels(data_unemp$Country)=='POL'] <- 'Poland'
levels(data_unemp$Country)[levels(data_unemp$Country)=='PRT'] <- 'Portugal'
levels(data_unemp$Country)[levels(data_unemp$Country)=='SVK'] <- 'Slovakia'
levels(data_unemp$Country)[levels(data_unemp$Country)=='ESP'] <- 'Spain'
levels(data_unemp$Country)[levels(data_unemp$Country)=='SWE'] <- 'Sweden'
levels(data_unemp$Country)[levels(data_unemp$Country)=='TUR'] <- 'Turkey'
levels(data_unemp$Country)[levels(data_unemp$Country)=='GBR'] <- 'UK'
levels(data_unemp$Country)[levels(data_unemp$Country)=='CHL'] <- 'Chile'
levels(data_unemp$Country)[levels(data_unemp$Country)=='EST'] <- 'Estonia'
levels(data_unemp$Country)[levels(data_unemp$Country)=='ISR'] <- 'Israel'
levels(data_unemp$Country)[levels(data_unemp$Country)=='SVN'] <- 'Slovenia'
levels(data_unemp$Country)[levels(data_unemp$Country)=='LVA'] <- 'Latvia'
levels(data_unemp$Country)[levels(data_unemp$Country)=='LTU'] <- 'Lithuania'
levels(data_unemp$Country)[levels(data_unemp$Country)=='COL'] <- 'Colombia'
```

# Change of the unemployment rate in G7 countries

The aim of this interactive graph is to capture the situation in G7 countries. It can be an important analysis due to the nature of these countries. The Group of Seven countries represent a large part of the global economy. \
Presented type of graph (Plotly) is usefull as it is easy and fast to capture the country (or countries) of interested as well as time horizon.

```{r gcountries, echo=FALSE, warning=FALSE, fig.align='center', fig.width = 10, fig.height = 6}

# Chosing G7 countries
plotly_data <- data_unemp %>%
  select(Country,TIME, Value) %>%
  filter(Country %in% c("USA", "Italy", "France", "Canada", "UK", "Germany", "Japan"))

g2 <- plotly_data %>%
  plot_ly(type = 'scatter'
          ,mode = 'lines'
          ,x = ~TIME
          ,y = ~Value
          ,color = ~Country
          ,colors = c('#00CED1','#4682B4','#228B22', '#8B008B', '#FF4500', '#FFD700', '#778899')
          ,text = ~Country
          ,hovertemplate = paste(
            "%{x|%Y/%m}<br>",
            "%{text}<br>",
            "%{y:,}%",
            "<extra></extra>")) %>%
  layout(yaxis = list(title="Unemployment rate in %"),
         xaxis = list(title="Date"),
         title = "G7 countries unemployment rate",
         legend = list(y = 0.5))

g2

```

In case of the coronavirus impact on the unemployment rate the most important are the dates related to 2020 and 2021. \
In our opinion the most interesting situation is in `r top_covid_countries[1,1]`, as it is a country with highest COVID-19 number of cases. 

# Unemployment rate in EU countries and Poland

The below graph can easily reflect the situation of Poland in comparison to the European Union countries during 2020. 

```{r, echo=FALSE, fig.align='center'}
plot_eur <- 
  data_unemp %>%
  filter(TIME %in% c("2020-01", "2020-02", "2020-03", "2020-04", "2020-05", "2020-06", "2020-07", "2020-08", "2020-09", "2020-10", "2020-11", "2020-12" )) %>%
  filter(Country == "EU27_2020" | Country == "Poland")%>%
  select(Country, Value, TIME) %>%
  cast(TIME~Country, value = 'Value') %>%
    ggplot( aes(x = TIME)) +
    geom_col(aes( y = EU27_2020, fill="EU countries")) +
    geom_text(aes(y = EU27_2020, label = paste0(round(EU27_2020,1),"%")), vjust = -0.5, color = "black", size = 3.2) +
    geom_line(aes(y = Poland, group = 1, color = "Poland"), size = 1.3) +
    scale_fill_manual(values=c("#00ace6", "black")) +
    scale_y_continuous(labels=function(x) paste0(x,"%")) +
    scale_x_discrete(labels=c("2020-01" = "1", "2020-02" = "2", "2020-03" = "3", "2020-04" = "4", "2020-05" = "5", "2020-06" = "6",
                              "2020-07" = "7", "2020-08" = "8", "2020-09" = "9", "2020-10" = "10", "2020-11" = "11", "2020-12" = "12")) +
    geom_text(aes(y = Poland, label = paste0(round(Poland,1),"%")), vjust = -0.5, color = "black", size = 3.2) +
    theme_minimal() +
    labs(title="Comparison of unemployment rate during 2020",
         subtitle = " between EU countries and Poland",
         y="Unemployment rate",
         x="Month")+
    theme(legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          plot.subtitle = element_text(hjust = 0.5, size =13))


plot_eur
```

From the graph one can observe that the unemployment rate in EU countries and also in Poland didn't change significantly. 
The impact of COVID-19 has no impact on unemployment rate in 2020 when it comes to EU countries and Poland.
The worst month is July, as the unemployment rate in European Union countries is equal to 7,8% and in Poland 3,4%.
Polish situation in comparison to European Union countries seems good as unemployment rate is significantly lower. 


# Country-specific unemployment rate
<font size="4">
One can chose any country and get country-specific report
<font>
```{r pressure, echo=FALSE,results='hide'}
country <- "POL"
rate <- read.csv("Dane/MW_new.csv")
rate <- rate[c(1, 3, 6, 7)]
rate <- transform(rate, TIME = as.Date(as.yearmon(TIME)))

eduk <- read.csv("Dane/eduk.csv", stringsAsFactors = FALSE)
eduk <- eduk[c(1, 3, 6, 7)]
eduk <- transform(eduk, TIME = as.Date(as.yearmon(TIME)))

agek <- read.csv("Dane/agek.csv")
agek <- agek[c(1, 3, 6, 7)]
agek <- transform(agek, TIME = as.Date(as.yearmon(TIME)))

unemp <- read.csv("Dane/unemp.csv")
unemp <- unemp[c(1, 6, 7)]
unemp <- transform(unemp, TIME = as.Date(as.yearmon(TIME)))
unemp <- subset(unemp, unemp$LOCATION == country)
unemp <- xts(unemp$Value, unemp$TIME)

unique(rate$X.LOCATION)
wide_DF <- subset(rate, rate$X.LOCATION == country)
wide_DF <- wide_DF %>% spread(SUBJECT, Value)
head(wide_DF, 24)
MEN <- xts(wide_DF$MEN, wide_DF$TIME)
WOMEN <- xts(wide_DF$WOMEN, wide_DF$TIME)
mw <- cbind(MEN, WOMEN)

eduk <- subset(eduk, eduk$LOCATION == country)
agek <- subset(agek, agek$LOCATION == country)

a <- dygraph(mw, main = paste("Unemployment rate in", country)) %>%
  dySeries("MEN", axis = "y2") %>%
  dyAxis(
    name = "y", independentTicks = T,
    axisLabelFormatter = "function(num){return num.toLocaleString() + '%'}",
    valueFormatter = "function(num){return num.toLocaleString() + '%'}"
  ) %>%
  dyAxis(
    name = "y2", independentTicks = T, drawGrid = T,
    axisLabelFormatter = "function(num){return num.toLocaleString() + '%'}",
    valueFormatter = "function(num){return num.toLocaleString() + '%'}"
  ) %>%
  dyEvent("2019-12-31", "First COVID case in world", labelLoc = "bottom") %>%
  dyEvent("2008-09-15", "Bankruptcy of Lehman Brothers", labelLoc = "bottom") %>%
  dyRangeSelector(dateWindow = c("2019-01-01", "2020-12-31"), fillColor = "#7570B3") %>%
  dyOptions(
    colors = RColorBrewer::brewer.pal(3, "Dark2"), axisLineColor = "navy",
    gridLineColor = "lightblue"
  )

```

```{r a, echo=FALSE}
a
```

```{r pro, echo=FALSE,results='hide'}
edu <- eduk %>%
  ggplot(aes(x = TIME, y = Value, color = SUBJECT)) +
  geom_line(size = 1) +
  theme_light() +
  scale_color_brewer(palette = "Dark2", labels = c("Below upper secondary", "Tertiary", "Upper secondary")) +
  labs(
    x = "Year", y = "Unemployment Rate",
    title = paste("By education level(", country, ")")
  ) +
  theme(
    plot.title = element_text(hjust = 1, size = 19, face = "bold.italic"),
    axis.title.x = element_text(size = 10, face = "bold.italic"),
    axis.title.y = element_text(size = 10, face = "bold.italic"),
    legend.title = element_blank(),
    legend.position = "bottom"
  ) +
  scale_y_continuous(label = function(x) {
    return(paste(x, "%"))
  })


age <- agek %>%
  ggplot(aes(x = TIME, y = Value, color = SUBJECT)) +
  geom_line(size = 1) +
  theme_light() +
  scale_color_brewer(palette = "Dark2", labels = c("15-24", "25-74")) +
  labs(
    x = "Year", y = "Unemployment Rate",
    title = paste("By age(", country, ")")
  ) +
  theme(
    plot.title = element_text(hjust = 1, size = 19, face = "bold.italic"),
    axis.title.x = element_text(size = 10, face = "bold.italic"),
    axis.title.y = element_text(size = 10, face = "bold.italic"),
    legend.title = element_blank(),
    legend.position = "bottom"
  ) +
  scale_y_continuous(label = function(x) {
    return(paste(x, "%"))
  })

mycolors <- c(brewer.pal(name = "Dark2", n = 8), brewer.pal(name = "Paired", n = 8))
```

```{r final graphs, echo=FALSE}
plot_grid(edu, age,rel_heights = c(1.9,2) )
```

## Forecast

We also did some forecasting using ARIMA. We used function auto-arima to find the best parameters.
```{r f, echo=FALSE}
head(unemp)
UR_ts <- ts(unemp[, 1], start = c(1997, 1), frequency = 12)
autoplot(UR_ts)
autoplot(diff(UR_ts))
ggAcf(diff(UR_ts))

# Find value for lamda to transform data and stablize variance
# See DataCamp/Forecasting Using R/Forecasting with ARIMA/Transformation for variance stabilization
# Lamda should range bt -1 (strong transformation, inverse) and 1 (no transformation)
bc <- BoxCox.lambda(UR_ts)
bc
ifelse(bc > -1 & bc < 1, "ok", "not ok")
# Fit a seasonal ARIMA model
fit1 <- auto.arima(UR_ts, trace = TRUE)
fit2 <- auto.arima(UR_ts, stepwise = FALSE)
# stepwise = FALSE to make auto.arima() work harder to find a good model from a larger collection of models

# Summarize the fitted model
summary(fit1)
summary(fit2)

with_theme_light <- function(expr) {
  orig <- theme_get()
  theme_set(theme_cowplot())
  force(expr)
  theme_set(orig)
}

with_theme_light(checkresiduals(fit1, color = "red", size = 2))
with_theme_light(checkresiduals(fit2, color = "red", size = 2))
checkresiduals(fit1)
checkresiduals(fit2)

# Plot 2-year forecasts
fit1 %>% forecast(h = 24)

fit2 %>% forecast(h = 24)

arima1 <- fit1 %>%
  forecast(h = 24) %>%
  autoplot() + theme_cowplot() + xlab("Date") + ylab("Unemployment Rate") +
  scale_y_continuous(limits = c(0, NA), label = function(x) {
    return(paste(x, "%"))
  })
arima2 <- fit2 %>%
  forecast(h = 24) %>%
  autoplot() + theme_cowplot() + xlab("Date") + ylab("Unemployment Rate") +
  scale_y_continuous(limits = c(0, NA), label = function(x) {
    return(paste(x, "%"))
  })

plot_grid(arima1, arima2)
```

We can see that the residuals are normally distributed and we can forecast.
By both models unemployment will go down and it is in line with our expectations.
